**Evaluation of machine learning methods for 16S rRNA gene data**

### 2019-05-22 submission/manuscript.Rmd
update to figures and paper and abstract:

Advances in sequencing technology and decreasing costs of generating 16S rRNA gene sequences have allowed rapid exploration of human associated microbiome and its health implications. Currently, the human microbiome field is growing at an unprecedented rate and as a result, there is an increasing demand for methods that identify associations between members of the microbiome and human health. However, this is difficult as human associated microbial communities are remarkably complex and uneven. It is unlikely that a single species can explain a disease. Instead, subsets of those communities, in relation to one another and to their host, account for the differences in health outcomes. Machine learning (ML) methods are effective at recognizing and highlighting patterns in complex microbial datasets. Therefore, researchers have started to explore the utility of ML models that use microbiota associated biomarkers to predict human health and to understand the microbial ecology of diseases such as liver cirrhosis, colorectal cancer, inflammatory bowel diseases (IBD), obesity, type 2 diabetes and others [@zeller_potential_2014; @zackular_human_2014; @baxter_dna_2016; @baxter_microbiota-based_2016; @hale_shifts_2017; @pasolli_machine_2016; @sze_looking_2016; @walters_meta-analyses_2014; @vazquez-baeza_guiding_2018; @qin_alterations_2014; @geman_deep_2018].  However, currently the field's use of ML lacks clarity and consistency on which methods are used and how these methods are implemented [@thaiss_persistent_2016;  . More notably, there are flawed ML practices like using ML pipelines where there is no seperate held-out test dataset to evaulate model performance, reporting few or only the best outcomes of different randomizations of cross-validation and showing a disregard for large differences between cross-validation and testing performances as well as large confidence intervals of testing performances [@flemer_oral_2018; @baxter_microbiota-based_2016; @dai_multi-cohort_2018; @montassier_pretreatment_2016; @papa_non-invasive_2012; @mossotto_classification_2017; @ai_systematic_2017; @wong_quantitation_2017]. Moreover, there is a lack of discussion on why a particular ML model is utilized. Recently, there is a trend towards using more complex ML models such as random forest, extreme gradient boosting and neural networks without a discussion on if and how much model interpretibility is necessary for the study [@galkin_human_2018; @reiman_using_2017; @fioravanti_phylogenetic_2017; @ @geman_deep_2018]. The lack of transparency on modeling methodology and model selection negatively impact model reproducibility and reliability. We need to strive toward better machine learning practices by (1) implementing consistent and reliable machine learning pipelines; (2) selecting ML models that reflect the goal of the study as it will inform our expectations of model accuracy, complexity, interpretibility and computational efficiency.

@@

We used a cohort of 490 patients with 261 cases of SRN. For each patient, we had `r paste(ncol(data)-1)` features (fecal bacterial abundances) and a two-class label that defines their colonic health (SRN or normal). All the cases were independently labeled through colonoscopies. We established modeling pipelines for a binary prediction task with L2-regularized logistic regression, L1 and L2 support vector machines (SVM) with linear and radial basis function kernels, a decision tree, random forest and XGBoost to emphasize the differences in  model accuracy, complexity, interpretibility and computational efficiency due to  model selection. We randomly split the data into training/validation and test sets so that the training/validation set consisted of 80% of the full dataset while the test set was composed of the remaining data [Figure 1]. Since the cases are not uniformly represented in the data, the initial data-split was stratified to maintain the overall label distribution on both the training/validation and test sets. Training/validation set consisted of 393 patients (209 SRN), while the test set was composed of 97 patients (52 SRN). The training/validation data was used for training purposes and validation of hyperparameter selection, and the test set was used for evaluation purposes. Validation of hyperparameter selection was performed using 100 randomizations of five-fold cross-validation on the training/validation set [Figure 1]. Similar to the initial data-split, five-fold cross-validation was also stratified to maintain the overall label distribution on the training and validation sets. We validated the cross-validation performances of each hyperparameter setting over the 100 randomizations and selected the best performing hyper-parameter setting to train the full training/validation dataset [Figures S1 and S2]. We then used the held-out test set to evaluate the prediction performance of each ML model. The data-split, hyperparameter selection, training and testing steps were repeated 100 times to get a reliable and robust reading of model prediction performance [Figure 1].

__Random forest has the highest prediction performance when applied to the held-out test data compared the other six ML models .__

We evaluated the prediction performances of seven binary classification models when applied to held-out test data using the area under the receiver operating characteristic curve (AUROC) as the discriminative performance metric. Random forest had significantly higher test AUROC values than the other models for detecting SRNs. The median AUROC of random forest was `r paste(round(median((all %>% filter(model=="Random_Forest"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="Random_Forest"))$test_aucs), 3))`). L2 logistic regression, XGBoost, L2 SVM with linear and radial basis function kernel AUROC values were not significantly different from one another. They had median AUROC values of `r paste(round(median((all %>% filter(model=="L2_Logistic_Regression"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L2_Logistic_Regression"))$test_aucs), 3))`), `r paste(round(median((all %>% filter(model=="XGBoost"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="XGBoost"))$test_aucs), 3))`), `r paste(round(median((all %>% filter(model=="L2_Linear_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L2_Linear_SVM"))$test_aucs), 3))`) and  `r paste(round(median((all %>% filter(model=="RBF_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="RBF_SVM"))$test_aucs), 3))`) respectively. L1 SVM with linear kernel and decision tree had significantly lower AUROC values than the other ML models with median AUROC of `r paste(round(median((all %>% filter(model=="L1_Linear_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L1_Linear_SVM"))$test_aucs), 3))`) and `r paste(round(median((all %>% filter(model=="Decision_Tree"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="Decision_Tree"))$test_aucs), 3))`), respectively [Figure 2].

__Predictive performances of the seven ML models during cross-validation and when applied to the held-out test data do not show large differences.__

We evaluated the generalization performance of each ML model by comparing their median cross-validation AUROC and median testing AUROC. The largest difference between the two was `r paste(round(abs(difference_model[difference_index[7],1]), 3))` in L1 SVM with linear kernel followed by SVM with radial basis function kernel and decision tree with a difference of `r paste(round(abs(difference_model[difference_index[6],1]), 3))` and `r paste(round(abs(difference_model[difference_index[5],1]), 3))`, respectively.

__The complexity and interpretibility of each ML model.__

The ML models we built using L2-regularized logistic regression, L1 and L2 support vector machines (SVM) with linear and radial basis function kernels, a decision tree, random forest and XGBoost increase in complexity as they decrase in interpretibility. We interpreted L1 and L2 SVM with linear kernel using the feature weights and L2 logistic regression using regression coefficients of the trained models. We calculated the mean weights and coefficients of all the features over the 100 data-splits. In the three linear models, OTUs that had the largest mean weights and drove the detection of SRNs belong to family *Lachnospiraceae*,  and *Ruminococcaceae* (OTU01239, OTU00659, OTU00742, OTU00012, OTU00050, OTU00015, OTU00768, OTU00822, OTU00609, OTU01212, OTU00629) and genera *Gamella*  (OTU00426) [Figure 3]. We explained the feature importances in non-linear models using permutation importance on the held-out test data. For the tree-based models, permuting *Peptostreptococcus* (OTU00367) abundances randomly, dropped the predictive performances the most. Decision tree, random forest and XGBoost models' predictive performance dropped from `r paste(round(dt_median, 2))` base testing AUROC median to `r paste(round(median((dt_imp %>% filter(names=="Otu00367"))$new_auc), 2))`, from `r paste(round(rf_median, 2))` to `r paste(round(median((rf_imp %>% filter(names=="Otu00367"))$new_auc), 2))` and from `r paste(round(xgboost_median, 2))` to `r paste(round(median((xgboost_imp %>% filter(names=="Otu00367"))$new_auc), 2))`, respectively [Figure 4]. The negative predictive impact of *Peptostreptococcus* in the decision tree model was followed by a *Lachnospiraceae* species (OTU00058) (`r paste(round(dt_median, 2))` base testing AUROC median to `r paste(round(median((dt_imp %>% filter(names=="Otu00058"))$new_auc), 2))`) [Figure 4B]. Other OTUs had none to minimal effect on the predictive performance.

@@

#### Interpretation of results
 Our results show that 
 Suprisingly, l2 logistic..
 computational efficiency and interp of logistic vs random forest
 decision tree and l1 why so low?

#### Consideration of possible weaknesses
 What happens with imbalanced data
 What happens with smaller datasets
 Does the code work on any microbiome data?
  Why did we use only one dataset? Becuase we are comparing several methods on 1 dataset.
  What will the future data look like?

@@

\newpage
\includegraphics{Figure_1}
**Figure 1. Machine learning pipeline showing predictive model training and evaluation flowchart.  **  We split the data 80%/20% stratified to maintain the overall label distribution, performed five-fold cross-validation on the training data to select the best hyperparameter setting and then using these hyperparameters to train all of the training data. The model was evaluated on a held-out set of data (not used in selecting the model).
Abbreviations: AUROC, area under the receiver operating characteristic curve
\newpage
\includegraphics{Figure_2.png}
**Figure 2. Generalization and classification performance of ML models using AUROC values of all cross validation and testing performances. **   The median AUROC for diagnosing individuals with SRN using bacterial abundances was higher than chance (depicted by horizontal line at 0.50) for all the ML models. Discriminative performance of random forest model was higher than other ML models. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: SRN, screen-relevant neoplasias; AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting
\newpage
\includegraphics{Figure_3.png}
**Figure 3. Interpretation of the linear ML models.** (A) L2 logistic regression coefficients  (B) L1 SVM with linear kernel feature weights (C) L2 SVM with linear kernel feature weights. The means weights and coefficients of the most important five OTUs for each model are shown here with the standard deviation over 100 data-splits. Similar OTUs had the largest impact on the predictive performance of L2 logistic regression and L2 SVM with linear kernel. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_4.png}
**Figure 4. Explanation of the non-linear ML models.** (A) SVM with radial basis kernel (B) decision tree (C) random forest (D) XGboost feaure importances were explanied using permutation importance using held-out test set. The gray rectangle and the dashed line show the IQR range and median of the base testing AUROC without any permutation performed. For all the tree-based models, a *Peptostreptococcus* species (OTU00367) had the largest impact on predictive performance of the model. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit; RBF, radial basis kernel; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_5.png}
**Figure 5. Computational efficiency of seven ML models.** The walltimes for training and testing of each data-split showed the differences in computational efficieny of the seven models. The median walltime in hours was the highest for XGBoost and shortest for L2 logistic regression. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting.  
\newpage

>>>>

Advances in sequencing technology and decreasing costs of generating 16S rRNA gene sequences have allowed rapid exploration of human associated microbiome and its health implications. Currently, the human microbiome field is growing at an unprecedented rate and as a result, there is an increasing demand for methods that identify associations between members of the microbiome and human health. However, this is difficult as human associated microbial communities are remarkably complex and uneven. It is unlikely that a single species can explain a disease. Instead, subsets of those communities, in relation to one another and to their host, account for the differences in health outcomes. Machine learning (ML) methods are effective at recognizing and highlighting patterns in complex microbial datasets. Therefore, researchers have started to explore the utility of ML models that use microbiota associated biomarkers to predict human health and to understand the microbial ecology of diseases such as liver cirrhosis, colorectal cancer, inflammatory bowel diseases (IBD), obesity, type 2 diabetes and others [@zeller_potential_2014; @zackular_human_2014; @baxter_dna_2016; @baxter_microbiota-based_2016; @hale_shifts_2017; @pasolli_machine_2016; @sze_looking_2016; @walters_meta-analyses_2014; @vazquez-baeza_guiding_2018; @qin_alterations_2014; @geman_deep_2018].  However, currently the field's use of ML lacks clarity and consistency on which methods are used and how these methods are implemented [@thaiss_persistent_2016;  . More notably, flawed ML practices are prevalent such as using ML pipelines where there is no seperate held-out test dataset to evaulate model performance, reporting few or only the best outcomes of different randomizations of cross-validation and showing a disregard for large differences between cross-validation and testing performances as well as large confidence intervals of testing performances [@flemer_oral_2018; @baxter_microbiota-based_2016; @dai_multi-cohort_2018; @montassier_pretreatment_2016; @papa_non-invasive_2012; @mossotto_classification_2017; @ai_systematic_2017; @wong_quantitation_2017]. Moreover, there is a lack of discussion on why a particular ML model is utilized. Recently, there is a trend towards using more complex ML models such as random forest, extreme gradient boosting and neural networks without a discussion on if and how much model interpretibility is necessary for the study [@galkin_human_2018; @reiman_using_2017; @fioravanti_phylogenetic_2017; @ @geman_deep_2018]. The lack of transparency on modeling methodology and model selection negatively impact model reproducibility and reliability. We need to strive toward better machine learning practices by (1) implementing consistent and reliable machine learning pipelines; (2) selecting ML models that reflect the goal of the study as it will inform our expectations of model accuracy, complexity, interpretibility and computational efficiency.

@@

We used a cohort of 490 patients with 261 cases of SRN. For each patient, we had `r paste(ncol(data)-1)` features (fecal bacterial abundances) and a two-class label that defines their colonic health (SRN or normal). All the cases were independently labeled through colonoscopies. We established modeling pipelines for a binary prediction task with L2-regularized logistic regression, L1 and L2 support vector machines (SVM) with linear and radial basis function kernels, a decision tree, random forest and extreme gradient boosted decision tree (XGBoost) to emphasize the differences in  model accuracy, complexity, interpretibility and computational efficiency due to  model selection.

For regularized logistic regression and SVM with linear kernel we used L2 regularization to keep all potentially important features. For comparison, we also trained an L1 regularized SVM model with linear kernel. L1-regularization on microbiome data lead to a sparser solution (i.e., force many coefficients to zero), removing features that could be correlated with other important features, making it more difficult include the relationships between the microbes and possibly dropping features that are important in detecting SRNs. Finally, to explore the potential for non-linear relationships among features and the outcome of interest, we trained tree based models, decision tree, random forest and XGboost, as well as an SVM with non-linear kernel.

We established a robust and reliable ML pipeline where we train and validate each of the seven models [Figure 1]. We randomly split the data into training/validation and test sets so that the training/validation set consisted of 80% of the full dataset while the test set was composed of the remaining data [Figure 1]. Since the cases are not uniformly represented in the data, the initial data-split was stratified to maintain the overall label distribution on both the training/validation and test sets. Training/validation set consisted of 393 patients (209 SRN), while the test set was composed of 97 patients (52 SRN). The training/validation data was used for training purposes and validation of hyperparameter selection, and the test set was used for evaluation purposes. Validation of hyperparameter selection was performed using 100 randomizations of five-fold cross-validation on the training/validation set [Figure 1]. Similar to the initial data-split, five-fold cross-validation was also stratified to maintain the overall label distribution on the training and validation sets. We validated the cross-validation performances of each hyperparameter setting over the 100 randomizations and selected the best performing hyper-parameter setting to train the full training/validation dataset [Figures S1 and S2]. We then used the held-out test set to evaluate the prediction performance of each ML model. The data-split, hyperparameter selection, training and testing steps were repeated 100 times to get a reliable and robust reading of model prediction performance [Figure 1].

__Model performance and generalizability.__

We evaluated the prediction performances of seven binary classification models when applied to held-out test data using the area under the receiver operating characteristic curve (AUROC) as the discriminative performance metric [Figure 1]. Random forest had significantly higher test AUROC values than the other models for detecting SRNs. The median AUROC of random forest was `r paste(round(median((all %>% filter(model=="Random_Forest"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="Random_Forest"))$test_aucs), 3))`). L2 logistic regression, XGBoost, L2 SVM with linear and radial basis function kernel AUROC values were not significantly different from one another. They had median AUROC values of `r paste(round(median((all %>% filter(model=="L2_Logistic_Regression"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L2_Logistic_Regression"))$test_aucs), 3))`), `r paste(round(median((all %>% filter(model=="XGBoost"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="XGBoost"))$test_aucs), 3))`), `r paste(round(median((all %>% filter(model=="L2_Linear_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L2_Linear_SVM"))$test_aucs), 3))`) and  `r paste(round(median((all %>% filter(model=="RBF_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="RBF_SVM"))$test_aucs), 3))`) respectively. L1 SVM with linear kernel and decision tree had significantly lower AUROC values than the other ML models with median AUROC of `r paste(round(median((all %>% filter(model=="L1_Linear_SVM"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="L1_Linear_SVM"))$test_aucs), 3))`) and `r paste(round(median((all %>% filter(model=="Decision_Tree"))$test_aucs), 3))` (IQR `r paste(round(IQR((all %>% filter(model=="Decision_Tree"))$test_aucs), 3))`), respectively [Figure 2].

We evaluated the generalization performance of each ML model by comparing their median cross-validation AUROC and median testing AUROC. This difference should be low to suggest the model is not overfitting despite the large number of features. The largest difference between the two was `r paste(round(abs(difference_model[difference_index[7],1]), 3))` in L1 SVM with linear kernel followed by SVM with radial basis function kernel and decision tree with a difference of `r paste(round(abs(difference_model[difference_index[6],1]), 3))` and `r paste(round(abs(difference_model[difference_index[5],1]), 3))`, respectively [Figure 2].

__Interpretation of each ML model.__

The ML models we built using L2-regularized logistic regression, L1 and L2 support vector machines (SVM) with linear and radial basis function kernels, a decision tree, random forest and XGBoost increase in complexity as they decrase in interpretibility. We interpreted L1 and L2 SVM with linear kernel using the feature weights and L2 logistic regression using regression coefficients of the trained models. We examined the 5 predictive (highest weight) and protective (lowest weight) features identified by the model. We calculated the mean weights and coefficients of these features over the 100 data-splits. In the three linear models, OTUs that had the largest mean weights and drove the detection of SRNs belong to family *Lachnospiraceae*,  and *Ruminococcaceae* (OTU01239, OTU00659, OTU00742, OTU00012, OTU00050, OTU00015, OTU00768, OTU00822, OTU00609, OTU01212, OTU00629) and genera *Gamella*  (OTU00426) [Figure 3]. We explained the feature importances in non-linear models using permutation importance on the held-out test data. For the tree-based models, permuting *Peptostreptococcus* (OTU00367) abundances randomly, dropped the predictive performances the most. Decision tree, random forest and XGBoost models' predictive performance dropped from `r paste(round(dt_median, 2))` base testing AUROC median to `r paste(round(median((dt_imp %>% filter(names=="Otu00367"))$new_auc), 2))`, from `r paste(round(rf_median, 2))` to `r paste(round(median((rf_imp %>% filter(names=="Otu00367"))$new_auc), 2))` and from `r paste(round(xgboost_median, 2))` to `r paste(round(median((xgboost_imp %>% filter(names=="Otu00367"))$new_auc), 2))`, respectively [Figure 4]. The negative predictive impact of *Peptostreptococcus* in the decision tree model was followed by a *Lachnospiraceae* species (OTU00058) (`r paste(round(dt_median, 2))` base testing AUROC median to `r paste(round(median((dt_imp %>% filter(names=="Otu00058"))$new_auc), 2))`) [Figure 4B]. Other OTUs had none to minimal effect on the predictive performance.

@@

#### Interpretation of results
 In this study we established a robust ML pipeline to use 16S rRNA sequence counts to predict a binary health outcome. We showed the importance of held-out test set and reporting the results of many iterations of cross-validation and testing. Each data-split has a weight that comes from random splitting. Seeing that testing and cross-validation median differences being low show that the models are generalizable and the pipeline works. Our results also show that we can choose different models for different reasons. Getting feature importances as weights and regression coefficients is the fastest and easiest interpratation. Similarly, linear models require less computational burden, fastest to train. THinking about the applicability, and actionability of a model in clinical setting, we might want faster results.

 Suprisingly, l2 logistic regression does really well. 
 computational efficiency and interp of logistic vs random forest
 decision tree and l1 why so low?

#### Consideration of possible weaknesses
 What happens with imbalanced data
 What happens with smaller datasets
 Does the code work on any microbiome data?
  Why did we use only one dataset? Why not validate on other data instead of held-out testing set? Becuase we are comparing several methods on 1 dataset.
  What will the future data look like?

@@

\newpage
\includegraphics{Figure_1}
**Figure 1. Machine learning pipeline showing predictive model training and evaluation flowchart.  **  We split the data 80%/20% stratified to maintain the overall label distribution, performed five-fold cross-validation on the training data to select the best hyperparameter setting and then using these hyperparameters to train all of the training data. The model was evaluated on a held-out set of data (not used in selecting the model).
Abbreviations: AUROC, area under the receiver operating characteristic curve
\newpage
\includegraphics{Figure_2.png}
**Figure 2. Generalization and classification performance of ML models using AUROC values of all cross validation and testing performances. **   The median AUROC for diagnosing individuals with SRN using bacterial abundances was higher than chance (depicted by horizontal line at 0.50) for all the ML models. Discriminative performance of random forest model was higher than other ML models. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: SRN, screen-relevant neoplasias; AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting
\newpage
\includegraphics{Figure_3.png}
**Figure 3. Interpretation of the linear ML models.** (A) L2 logistic regression coefficients  (B) L1 SVM with linear kernel feature weights (C) L2 SVM with linear kernel feature weights. The means weights and coefficients of the most important five OTUs for each model are shown here with the standard deviation over 100 data-splits. Similar OTUs had the largest impact on the predictive performance of L2 logistic regression and L2 SVM with linear kernel. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_4.png}
**Figure 4. Explanation of the non-linear ML models.** (A) SVM with radial basis kernel (B) decision tree (C) random forest (D) XGboost feaure importances were explanied using permutation importance using held-out test set. The gray rectangle and the dashed line show the IQR range and median of the base testing AUROC without any permutation performed. For all the tree-based models, a *Peptostreptococcus* species (OTU00367) had the largest impact on predictive performance of the model. 
Abbreviations: SVM, support vector machine; OTU, Operational Taxonomic Unit; RBF, radial basis kernel; OTU, Operational Taxonomic Unit.
\newpage
\includegraphics{Figure_5.png}
**Figure 5. Computational efficiency of seven ML models.** The walltimes for training and testing of each data-split showed the differences in computational efficieny of the seven models. The median walltime in hours was the highest for XGBoost and shortest for L2 logistic regression. The boxplot shows quartiles at the box ends and the statistical median as the horizontal line in the box. The whiskers show the farthest points that are not outliers. Outliers are data points that are not within 3/2 times the interquartile ranges. 
Abbreviations: AUROC, area under the receiver operating characteristic curve; SVM, support vector machine; XGBoost, extreme gradient boosting.  
\newpage
\includegraphics{Figure_S1.png}
**Figure S1. Hyperparameter setting performances for linear models.** 
Abbreviations: 
\newpage
\includegraphics{Figure_S2.png}
**Figure S2. Hyperparameter setting performances for non-linear models.** 
Abbreviations: 
\newpage
